% ==================== 参考文献 ====================
\clearpage
\section*{参考文献}
\addcontentsline{toc}{section}{参考文献}

\begin{enumerate}[leftmargin=2em,itemsep=0.3em]
  \item Burke E K, Petrovic S. Recent research directions in automated
    timetabling[J]. European Journal of Operational Research,
    2002, 140(2): 266--280.

  \item de Werra D. Scheduling in sports[M]//Studies in Integer
    Programming. North-Holland, 1977: 381--395.

  \item Google OR-Tools Team. OR-Tools: Software for Combinatorial
    Optimization[EB/OL]. \url{https://developers.google.com/optimization},
    2024.

  \item Rossi F, van Beek P, Walsh T. Handbook of Constraint
    Programming[M]. Elsevier, 2006.

  \item Apt K. Principles of Constraint Programming[M]. Cambridge
    University Press, 2003.

  \item Laborie P, Rogerie J, Shaw P, et al. Reasoning with
    conditional time-intervals[C]//Proceedings of the Twenty-First
    International Florida Artificial Intelligence Research Society
    Conference. 2008: 555--560.

  \item 中国教育部. 关于进一步减轻义务教育阶段学生作业负担和
    校外培训负担的意见[Z]. 2021.

  \item 字节跳动飞书团队. 飞书开放平台开发者文档[EB/OL].
    \url{https://open.feishu.cn/document}, 2024.

  \item Cormen T H, Leiserson C E, Rivest R L, et al. Introduction
    to Algorithms (4th ed.)[M]. MIT Press, 2022.

  \item Taha H A. Operations Research: An Introduction (10th ed.)[M].
    Pearson, 2017.

  \item Python Software Foundation. The Python Language Reference
    (3.12)[EB/OL]. \url{https://docs.python.org/3.12/}, 2024.

  \item 维基百科. Constraint Programming[EB/OL].
    \url{https://en.wikipedia.org/wiki/Constraint_programming},
    2024.

  \item Russell S, Norvig P. Artificial Intelligence: A Modern
    Approach (4th ed.)[M]. Pearson, 2020.
\end{enumerate}
